Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression

### 2019-01-09 04-ADMMsigma-Package.Rmd
restructed manuscript

# `ADMMsigma` Tutorial

In many statistical applications, estimating the covariance for a set of random variables is a critical task. The covariance is useful because it characterizes the *relationship* between variables. For instance, suppose we have three variables $X, Y, \mbox{ and } Z$ and their covariance matrix is of the form

\[ \Sigma_{xyz} = \begin{pmatrix}
1 & 0 & 0.5 \\ 
0 & 1 & 0 \\ 
0.5 & 0 & 1
\end{pmatrix} \]

We can gather valuable information from this matrix. First of all, we know that each of the variables has an equal variance of 1. Second,  we know that variables $X$ and $Y$ are likely independent because the covariance between the two is equal to 0. This implies that any information in $X$ is useless in trying to gather information about $Y$. Lastly, we know that variables $X$ and $Z$ are moderately, positively correlated because their covariance is 0.5.

Unfortunately, estimating $\Sigma$ well is often computationally expensive and, in a few settings, extremely challenging. For this reason, emphasis in the literature and elsewhere has been placed on estimating the inverse of $\Sigma$ which we like to denote as $\Omega \equiv \Sigma^{-1}$.

>>>>

# `ADMMsigma` R Package

### 2019-01-09 index.Rmd
restructed manuscript

--- 
title: "Oral Manuscript"
author: "Matt Galloway"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
#bibliography: [lib.bib, packages.bib]
bibliography: lib.bib
biblio-style: apalike
colorlinks: yes
lot: no
lof: no
fontsize: 11pt
link-citations: yes
#url: 'https://mgallow.github.io/oral_manuscript/'
github-repo: MGallow/oral_manuscript
description: "This is a working manuscript in preparation for Matt Galloway's doctoral oral examination."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, tidy = TRUE)

# ```{r include=FALSE}
# # automatically create a bib database for R packages
# knitr::write_bib(c(
#   .packages(), 'bookdown', 'knitr', 'rmarkdown'
# ), 'packages.bib')
# ```

@@

# Prerequisites

>>>>

--- 
title: "Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression"
author: "Matt Galloway"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output:
  bookdown::pdf_book:
    toc_depth: 2
    fig_caption: yes
    includes:
      in_header: preamble.tex
  bookdown::gitbook:
    toc_depth: 2
documentclass: report
bibliography: [lib.bib, packages.bib]
#bibliography: lib.bib
biblio-style: apalike
#geometry: "left=4cm, right=3cm, top=2.5cm, bottom=2.5cm"
#geometry: "left = 1.5in, right = 1in, top = 1in, bottom = 1in"
geometry: "left = 1in, right = 1in, top = 1in, bottom = 1in"
colorlinks: yes
lot: no
lof: no
toc_appendix: yes
fontsize: 11pt
linestretch: 1.5
link-citations: yes
#url: 'https://mgallow.github.io/oral_manuscript/'
github-repo: MGallow/oral_manuscript
description: "This is a working manuscript in preparation for Matt Galloway's master's thesis defense."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, tidy = TRUE, out.width = "90%", fig.align = "center", out.extra = "")

@@

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(.packages(), "glasso", "ADMMsigma", "SCPME"), 'packages.bib')
